\documentclass{beamer}
\usepackage{graphicx}
\usepackage{booktabs}

\title{The Role of Firm R\&D Effort and Collaborations as Mediating Drivers of Innovation Policy Effectiveness}
\author{Giovanni Cerulli, Bianca Poti
IRCRES CNR,   Roberto Gabriele, 
Department of Economics and Management, University of Trento,  }
\date{}

\begin{document}

\frame{\titlepage}


\section{Types of Additionality}
\begin{frame}{Types of Additionality}
    \begin{itemize}
        \item \textbf{Input Additionality}: Increase in private spending due to government support.
        \item \textbf{Output Additionality}: Additional outputs resulting from subsidies.
        \item \textbf{Behavioral Additionality}: Long-term changes in how firms undertake R\&D.
    \end{itemize}
\end{frame}

\section{Research Question}
\begin{frame}{Research Question}
    \begin{itemize}
        \item Does behavioral additionality play a role?
        \item What is the transmission mechanism of such an effect?
        \item Specifically, we analyze \textit{collaboration performance} promoted by policy.
    \end{itemize}
\end{frame}

\section{Research Methodology}
\begin{frame}{Research Method 1}
    \begin{itemize}
        \item Treatment random coefficient model (Wooldridge, 2010) used.
        \item Step 1: Define Average Treatment Effect (ATE) conditional on covariates.
        \item Two effects estimated:
        \begin{itemize}
            \item ATE input: Effect of R\&D support on company R\&D.
            \item ATE behavioral: Effect on cooperation degree.
        \end{itemize}
    \end{itemize}
\end{frame}

\section{Data}
\begin{frame}{Data Sources}
    \begin{itemize}
        \item Panel of Italian manufacturing and services firms.
        \item Data from CIS 3 and 4 innovation surveys (1998-2004).
        \item AIDA dataset (company balance sheets).
    \end{itemize}
\end{frame}

\section{Results}
\begin{frame}{Behavioral Additionality Results}
    \begin{itemize}
        \item Strong significance of R\&D support on cooperation.
        \item ATE around 0.37.
        \item Regression analysis confirms impact.
    \end{itemize}
\end{frame}

\begin{frame}{Input Additionality Results}
    \begin{itemize}
        \item Significant effect of R\&D support on R\&D performance.
        \item ATE around 0.016.
    \end{itemize}
\end{frame}

\section{Conclusions}
\begin{frame}{Conclusions}
    \begin{itemize}
        \item Innovation is driven by R\&D cooperation facilitated by public support.
        \item Synergy exists between behavioral additionality and R\&D additionality.
        \item A threshold of cooperation is necessary for firms to benefit from R\&D support.
    \end{itemize}
\end{frame}

\end{document}
